LSOA domestic Electricty and Gas maps

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Adding plot of gas consumption against deprevation

```
####Plotting the change in gas usage against the deprevation 
```{r plotting change in gas usage against dep}
LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
names(LSOAdepgas)
df <- dplyr::select(LSOAdepgas, LSOA11CD, "Local Authority Name.x", dg_diff, IMDScore, dgas2010, IMD_Decile
)

@@

```{r addFacetsToElecDiff}
# or without colour but using facets for Local Authorities
Solentex <- filter(Solent,100*(dg_diff/dgas2010)<50)
ggplot(Solentex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/dgas2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change") +
  facet_wrap(`Local Authority Name.x` ~ .)

nrow(Solent)
```

####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)

>>>>

```
####Plotting the change in gas usage against the deprevation 
```{r plotting change in gas usage against dep}
LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
names(LSOAdepgas)
df <- dplyr::select(LSOAdepgas, LSOA11CD, "Local Authority Name.x", dg_diff, IMDScore, dgas2010, IMD_Decile, dgas2019
)

@@

```{r addFacetsTogasDiff}
# or without colour but using facets for Local Authorities
Solentex <- filter(Solent,100*(dg_diff/dgas2010)<50)
ggplot(Solentex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/dgas2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change") +
  facet_wrap(`Local Authority Name.x` ~ .)

nrow(Solent)
```
#####Plotting the gas usage against deprevation
```{r Boxplot of the gas consumption and deprevation}
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dgas2019, 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "Gas Consumption")

```
```{r addFacetsTogasconsumption}
# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dgas2019, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Gas Consumption") +
  facet_wrap(`Local Authority Name.x` ~ .)

nrow(Solent)
```
####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)
